Computational methods in landscape ecology

### 2024-05-15 Sections/introduction.qmd
Starting to move things around

---
title: "Computational methods in landscape ecology"
author:
  - name: Maximilian H.K. Hesselbarth
    orcid: 0000-0003-1125-9918
    email: mhk.hesselbarth@gmail.com
    affiliations:
      - name: International Institute for Applied Systems Analysis, Biodiversity, Ecology, and Conservation Group, Laxenburg (Austria)
bibliography: CLER.bib
format:
  pdf:
    keep-tex: true
    number-sections: true
    template-partials: 
      - title.tex
    include-in-header: 
      text: | 
        \usepackage{lineno}\linenumbers
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
---

@@

{{< pagebreak >}}

>>>>

---
bibliography: CLER.bib
---

<!-- Person responsible: Hesselbarth -->

@@
